Speed estimation for vehicles using \\SVM classification and edge detection

### 2016-06-14 Administratie/report/paper.tex
update report
title change

% first the title is needed
\title{Speed estimation using SVM classification and edge detection}

% a short form should be given in case it is too long for the running head
\titlerunning{Speed estimation using SVM classification and edge detection}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Mathias Dierickx\and Tim Ranson\and Maarten Tindemans\and Bjorn Vandenbussche}
%
\authorrunning{Speed estimation using SVM classification and *blablabla* line detection}
% (feature abused for this document to repeat the title also on left hand pages)

@@

For the implementation of our method, we use OpenCV 3.1 \cite{Bradski2000} and C++.

@@

The block size affects the level of detail taken into account while calculating the feature vector, as the values for the feature vector operate within one block size.

TODO: insert photos block sizes

>>>>

% first the title is needed
\title{Speed estimation for vehicles using \\SVM classification and edge detection}

% a short form should be given in case it is too long for the running head
\titlerunning{Speed estimation for vehicles using SVM classification and edge detection}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Mathias Dierickx\and Tim Ranson\and Maarten Tindemans\and Bjorn Vandenbussche}
%
\authorrunning{Speed estimation for vehicles using SVM classification and edge detection}
% (feature abused for this document to repeat the title also on left hand pages)

@@

For the implementation of our method, we use OpenCV 3.1 \cite{Bradski2000} and C++. Four different datasets were used to either or test the solution.

\textbf{TODO}: kort over training van classificatie  (TIM)

@@

The block size affects the level of detail taken into account while calculating the feature vector, as the values for the feature vector operate within one block size. Some examples of different block sizes can be found in figure \ref{fig:methods-block-sizes}.

TODO
